---
title: 'RSV Wastewater Surveillance in Georgia'
subtitle: 'DATA 550 Midterm Report'
author: 'Imani Allen, Linda Bueno Cinto, Alia Hiller, McKenzie Reese'
date: "`r format(Sys.Date(), '%b-%d-%y')`"
output: html_document

---
```{r, setup, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r, load-data}
here::i_am('rsv_report.Rmd')

data <- readRDS(
  file = here::here('output/00_load_data.rds')
)
```

# __Introduction__

Respiratory syncytial virus (RSV) is a common respiratory virus. It does not 
usually cause severe illness in healthy adults and children. However, some people
with RSV infection, especially infants younger than 6 months of age and adults who
are older or have certain risk factors, can become very sick and may need to be hospitalized.^1^
Wastewater monitoring can detect viruses spreading from one person to another
within a community earlier than clinical testing and before people who are sick
go to their doctor or hospital. It can also detect infections without symptoms.^2^
If you see increased wastewater viral activity levels, it might indicate that there is a higher risk of infection,
which can inform local public health response.

Data from this analysis is RSV wastewater surveillance from CDC subsetted to the state of Georgia. This analysis aims to:

* Provide descriptive analysis of county wastewater data
* Examine how RSV concentration in wastewater changes over time
* Analyze the relationship between a facility’s flow rate and the population served

# __Descriptive Analysis__

## Table 1

Table 1 provides descriptive analysis of county wastewater data.

```{r, table1}
table1 <- readRDS(
  file = here::here('output/01_table1.rds')
)

table1
```


## Figure 1

Figure 1 shows changes in RSV concentration in wastewater over time.

```{r, plot-data1}
#| fig.align = "center",
#| out.width = "600px"

knitr::include_graphics(
  here::here('output/02_scatterplot.png')
)
```

## Figure 2

Figure 2 shows the relationship between a facility’s flow rate and the population served.

```{r, plot-data2}
#| fig.align = "center",
#| out.width = "600px"

knitr::include_graphics(
  here::here('output/03_scatterplot2.png')
)
```
